Better fusion for filters

### 2014-04-01 2014betterfusionforfilters/section/01-Introduction.tex
Add note to intro
simplified ILP constraints
Adding citations

Recent work on data flow fusion~\cite{lippmeier2013data} shows how to compile a specific class of data flow programs into \emph{single}, efficient imperative loops. This process of ``compilation'' is equivalent to performing array fusion on a combinator based functional array program, as per related work on stream fusion~\cite{coutts2007streamfusion} and delayed arrays \cite{repa}. The key benefits of data flow fusion over prior work are that 1) it can fuse programs that use branching data flows where a produced array is consumed by several consumers, and 2) complete fusion is guaranteed for all programs that fall into the specific class that can be fused.

@@

However, many programs \emph{do} contain opportunities for fusion, if we only new which opportunities to take. The following function is similar to the one from before, except that it offers two unique \emph{but mutually exclusive} approaches to fusion:
\begin{code}
 normalizeInc :: Array Int -> Array Int
 normalizeInc xs
  = let incs = map  (+1)    us      (A1) (B2)
        sum  = fold (+) 0   us      (A1) (B1)
        norm = map  (/ sum) incs    (A2) (B2)
    in  norm
\end{code}

@@

\TODO{Briefly mention related work. Other approaches to typed fusion}

>>>>

Recent work on data flow fusion~\cite{lippmeier2013flow} shows how to compile a specific class of data flow programs into \emph{single}, efficient imperative loops. This process of ``compilation'' is equivalent to performing array fusion on a combinator based functional array program, as per related work on stream fusion~\cite{coutts2007streamfusion} and delayed arrays \cite{keller2010repa}. The key benefits of data flow fusion over prior work are that 1) it can fuse programs that use branching data flows where a produced array is consumed by several consumers, and 2) complete fusion is guaranteed for all programs that fall into the specific class that can be fused.

\ben{reword last sentence, reads like a tautology}

@@

However, many programs \emph{do} contain opportunities for fusion, if we only knew which opportunities to take. The following function is similar to the one from before, except that it offers two unique \emph{but mutually exclusive} approaches to fusion:

\TODO{If the main contribution is fusion for *filters* then we need to use a motivating example with a filter}

\begin{code}
 normalizeInc :: Array Int -> Array Int
 normalizeInc xs
  = let incs = map  (+1)    us      (A1) (B2)
        sum  = fold (+) 0   us      (A1) (B1)
        norm = map  (/ sum) incs    (A2) (B2)
    in  norm
\end{code}

@@

The reduction of the clustering problem to integer linear programming was previously described by \cite{megiddo1998weighted}, though they do not consider filtering operations.
